Windowed least-squares model reduction for dynamical systems

### 2019-10-24 main.tex
minor language changes

In the case of \spatialAcronym\ trial subspaces, \methodAcronym\ displays improved performance over Galerkin and LSPG projection at the expense of an increased computational cost. This increase in computational cost is due to the fact that forming and/or solving the nonlinear minimization problem becomes more difficult as the time window grows. To minimize this increase in cost, future work will target the development of new solution techniques tailored to \methodAcronym.

%The principal challenge encountered in the \methodAcronym\ formulation is the computational cost: increasing the window size over which the residual is minimized leads to a higher computational cost. In the context of the direct solution approach, this increased cost is due to the increased cost of forming and solving the least-squares problem associated with larger window sizes. In the context of indirect methods, this increased cost is a result of the increased number of iterations of the forward backward sweep method. While numerical experiments demonstrated that the increase in computational cost is mild, future work will focus on the development of solution techniques to improve the scaling of the method.

>>>>

%In the case of \spatialAcronym\ trial subspaces, \methodAcronym\ displays improved performance over Galerkin and LSPG projection at the expense of an increased computational cost. This increase in computational cost is due to the fact that forming and/or solving the nonlinear minimization problem becomes more difficult as the time window grows. To minimize this increase in cost, future work will target the development of new solution techniques tailored to \methodAcronym.

The principal challenge encountered in the \methodAcronym\ formulation is the computational cost: increasing the window size over which the residual is minimized leads to a higher computational cost. In the context of the direct solution approach, this increased cost is due to the increased expense of forming and solving the least-squares problem associated with larger window sizes. In the context of indirect methods, this increased cost is a result of the increased number of iterations of the forward backward sweep method. While numerical experiments demonstrated that the increase in computational cost is mild, future work will target the development of new solution techniques tailored for the \methodAcronym\ approach.
